Optimization model for multi-product multi-period multi-supplier raw-material selection and composition, and order quantity problem with minimum one-year order quantity contract

### 2023-03-09 Thesis/MethodX/Manuscript/Manuscript.tex
manuskrip final

\caption{One-year production planning and inventory control}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Decision proccess planning horizon}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{Illustration for inventory cost calculation}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-5}the flexibility matrix of items 1-25}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{6}{c}{Raw material} \\
\cline{2-7}
item & 1 & 2 & 3 & 4 & 5 & 6\\
\hline
1 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
2 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
3 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
4 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
5 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
6 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
7 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
8 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
9 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
10 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
11 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
12 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
13 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
14 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
15 & 1 & 0 & 0 & 1 & 0 & 0\\
\hline
16 & 1 & 0 & 0 & 1 & 0 & 0\\
\hline
17 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
18 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
19 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
20 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
21 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
22 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
23 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
24 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
25 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
\end{tabular}
\end{table}
\pagebreak

@@

\caption{\label{tab:unnamed-chunk-6}the flexibility matrix of items 26-51}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{6}{c}{Raw material} \\
\cline{2-7}
item & 1 & 2 & 3 & 4 & 5 & 6\\
\hline
26 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
27 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
28 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
29 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
30 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
31 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
32 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
33 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
34 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
35 & 1 & 1 & 0 & 1 & 0 & 1\\
\hline
36 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
37 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
38 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
39 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
40 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
41 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
42 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
43 & 1 & 1 & 1 & 1 & 0 & 1\\
\hline
44 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
45 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
46 & 1 & 1 & 0 & 1 & 0 & 1\\
\hline
47 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
48 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
49 & 0 & 0 & 0 & 1 & 0 & 0\\
\hline
50 & 0 & 0 & 0 & 1 & 0 & 0\\
\hline
51 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-7}the flexibility matrix of items 1-11}
\centering
\begin{tabular}[t]{r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{4}{c}{raw -material demand (in kg)} \\
\cline{2-5}
item & week 1 & week 2 & week 3 & week 4\\
\hline
1 & 2555.1 & 2555.1 & 0 & 10220.4\\
\hline
2 & 0.0 & 4300.0 & 8600 & 0.0\\
\hline
3 & 0.0 & 0.0 & 0 & 1800.0\\
\hline
4 & 0.0 & 495.0 & 0 & 0.0\\
\hline
5 & 0.0 & 0.0 & 0 & 0.0\\
\hline
6 & 3150.0 & 0.0 & 6300 & 0.0\\
\hline
7 & 0.0 & 1050.0 & 0 & 350.0\\
\hline
8 & 1650.0 & 0.0 & 0 & 2200.0\\
\hline
9 & 2080.0 & 1560.0 & 1040 & 0.0\\
\hline
10 & 0.0 & 1280.0 & 0 & 0.0\\
\hline
11 & 0.0 & 0.0 & 4200 & 0.0\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-8}the flexibility matrix of items 12-51}
\centering
\begin{tabular}[t]{r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{4}{c}{raw -material demand (in kg)} \\
\cline{2-5}
item & week 1 & week 2 & week 3 & week 4\\
\hline
12 & 0 & 2700 & 0 & 0\\
\hline
13 & 350 & 350 & 0 & 0\\
\hline
14 & 0 & 300 & 500 & 200\\
\hline
15 & 85 & 0 & 0 & 0\\
\hline
16 & 110 & 165 & 0 & 0\\
\hline
17 & 0 & 0 & 17400 & 17400\\
\hline
18 & 74050 & 222150 & 14800 & 0\\
\hline
19 & 0 & 11605 & 0 & 0\\
\hline
20 & 12750 & 0 & 0 & 0\\
\hline
21 & 3500 & 0 & 14000 & 14000\\
\hline
22 & 42100 & 0 & 10550 & 0\\
\hline
23 & 0 & 0 & 5600 & 11200\\
\hline
24 & 5400 & 5400 & 0 & 5400\\
\hline
25 & 1350 & 2250 & 0 & 0\\
\hline
26 & 0 & 32400 & 43200 & 0\\
\hline
27 & 10350 & 31050 & 0 & 0\\
\hline
28 & 118200 & 0 & 0 & 0\\
\hline
29 & 3330 & 4995 & 0 & 0\\
\hline
30 & 0 & 1950 & 0 & 5850\\
\hline
31 & 0 & 6300 & 6300 & 0\\
\hline
32 & 2310 & 3465 & 0 & 0\\
\hline
33 & 0 & 2500 & 0 & 0\\
\hline
34 & 0 & 0 & 20850 & 0\\
\hline
35 & 12150 & 0 & 0 & 0\\
\hline
36 & 0 & 0 & 0 & 0\\
\hline
37 & 12750 & 12750 & 8500 & 8500\\
\hline
38 & 1550 & 3100 & 0 & 0\\
\hline
39 & 0 & 10600 & 5300 & 21200\\
\hline
40 & 0 & 0 & 10450 & 20900\\
\hline
41 & 9625 & 0 & 1375 & 1375\\
\hline
42 & 0 & 0 & 3080 & 0\\
\hline
43 & 0 & 2250 & 450 & 2250\\
\hline
44 & 0 & 0 & 14100 & 0\\
\hline
45 & 6700 & 13400 & 10050 & 6700\\
\hline
46 & 6500 & 13000 & 0 & 0\\
\hline
47 & 26200 & 13100 & 0 & 0\\
\hline
48 & 12000 & 8000 & 0 & 12000\\
\hline
49 & 0 & 126 & 0 & 0\\
\hline
50 & 1323 & 0 & 3969 & 0\\
\hline
51 & 1170 & 1170 & 0 & 780\\
\hline
\end{tabular}
\end{table}

@@

@@

>>>>

\caption{One-year production planning and inventory control}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Decision proccess planning horizon}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Illustration for inventory cost calculation}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-4}the flexibility matrix of items 1-25}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{6}{c}{Raw material} \\
\cline{2-7}
item & 1 & 2 & 3 & 4 & 5 & 6\\
\hline
1 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
2 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
3 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
4 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
5 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
6 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
7 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
8 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
9 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
10 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
11 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
12 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
13 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
14 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
15 & 1 & 0 & 0 & 1 & 0 & 0\\
\hline
16 & 1 & 0 & 0 & 1 & 0 & 0\\
\hline
17 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
18 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
19 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
20 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
21 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
22 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
23 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
24 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
25 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
\end{tabular}
\end{table}
\pagebreak

@@

\caption{\label{tab:unnamed-chunk-5}the flexibility matrix of items 26-51}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{6}{c}{Raw material} \\
\cline{2-7}
item & 1 & 2 & 3 & 4 & 5 & 6\\
\hline
26 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
27 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
28 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
29 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
30 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
31 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
32 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
33 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
34 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
35 & 1 & 1 & 0 & 1 & 0 & 1\\
\hline
36 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
37 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
38 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
39 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
40 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
41 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
42 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
43 & 1 & 1 & 1 & 1 & 0 & 1\\
\hline
44 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
45 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
46 & 1 & 1 & 0 & 1 & 0 & 1\\
\hline
47 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
48 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
49 & 0 & 0 & 0 & 1 & 0 & 0\\
\hline
50 & 0 & 0 & 0 & 1 & 0 & 0\\
\hline
51 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-6}the flexibility matrix of items 1-11}
\centering
\begin{tabular}[t]{r|l|l|l|l}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{4}{c}{raw -material demand (in kg)} \\
\cline{2-5}
item & week 1 & week 2 & week 3 & week 4\\
\hline
1 & 2,555.1 & 2,555.1 & 0.0 & 10,220.4\\
\hline
2 & 0.0 & 4,300.0 & 8,600.0 & 0.0\\
\hline
3 & 0.0 & 0.0 & 0.0 & 1,800.0\\
\hline
4 & 0.0 & 495.0 & 0.0 & 0.0\\
\hline
5 & 0.0 & 0.0 & 0.0 & 0.0\\
\hline
6 & 3,150.0 & 0.0 & 6,300.0 & 0.0\\
\hline
7 & 0.0 & 1,050.0 & 0.0 & 350.0\\
\hline
8 & 1,650.0 & 0.0 & 0.0 & 2,200.0\\
\hline
9 & 2,080.0 & 1,560.0 & 1,040.0 & 0.0\\
\hline
10 & 0.0 & 1,280.0 & 0.0 & 0.0\\
\hline
11 & 0.0 & 0.0 & 4,200.0 & 0.0\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-7}the flexibility matrix of items 12-51}
\centering
\begin{tabular}[t]{r|l|l|l|l}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{4}{c}{raw-material demand (in kg)} \\
\cline{2-5}
item & week 1 & week 2 & week 3 & week 4\\
\hline
12 & 0.0 & 2,700.0 & 0.0 & 0.0\\
\hline
13 & 350.0 & 350.0 & 0.0 & 0.0\\
\hline
14 & 0.0 & 300.0 & 500.0 & 200.0\\
\hline
15 & 85.0 & 0.0 & 0.0 & 0.0\\
\hline
16 & 110.0 & 165.0 & 0.0 & 0.0\\
\hline
17 & 0.0 & 0.0 & 17,400.0 & 17,400.0\\
\hline
18 & 74,050.0 & 222,150.0 & 14,800.0 & 0.0\\
\hline
19 & 0.0 & 11,605.0 & 0.0 & 0.0\\
\hline
20 & 12,750.0 & 0.0 & 0.0 & 0.0\\
\hline
21 & 3,500.0 & 0.0 & 14,000.0 & 14,000.0\\
\hline
22 & 42,100.0 & 0.0 & 10,550.0 & 0.0\\
\hline
23 & 0.0 & 0.0 & 5,600.0 & 11,200.0\\
\hline
24 & 5,400.0 & 5,400.0 & 0.0 & 5,400.0\\
\hline
25 & 1,350.0 & 2,250.0 & 0.0 & 0.0\\
\hline
26 & 0.0 & 32,400.0 & 43,200.0 & 0.0\\
\hline
27 & 10,350.0 & 31,050.0 & 0.0 & 0.0\\
\hline
28 & 118,200.0 & 0.0 & 0.0 & 0.0\\
\hline
29 & 3,330.0 & 4,995.0 & 0.0 & 0.0\\
\hline
30 & 0.0 & 1,950.0 & 0.0 & 5,850.0\\
\hline
31 & 0.0 & 6,300.0 & 6,300.0 & 0.0\\
\hline
32 & 2,310.0 & 3,465.0 & 0.0 & 0.0\\
\hline
33 & 0.0 & 2,500.0 & 0.0 & 0.0\\
\hline
34 & 0.0 & 0.0 & 20,850.0 & 0.0\\
\hline
35 & 12,150.0 & 0.0 & 0.0 & 0.0\\
\hline
36 & 0.0 & 0.0 & 0.0 & 0.0\\
\hline
37 & 12,750.0 & 12,750.0 & 8,500.0 & 8,500.0\\
\hline
38 & 1,550.0 & 3,100.0 & 0.0 & 0.0\\
\hline
39 & 0.0 & 10,600.0 & 5,300.0 & 21,200.0\\
\hline
40 & 0.0 & 0.0 & 10,450.0 & 20,900.0\\
\hline
41 & 9,625.0 & 0.0 & 1,375.0 & 1,375.0\\
\hline
42 & 0.0 & 0.0 & 3,080.0 & 0.0\\
\hline
43 & 0.0 & 2,250.0 & 450.0 & 2,250.0\\
\hline
44 & 0.0 & 0.0 & 14,100.0 & 0.0\\
\hline
45 & 6,700.0 & 13,400.0 & 10,050.0 & 6,700.0\\
\hline
46 & 6,500.0 & 13,000.0 & 0.0 & 0.0\\
\hline
47 & 26,200.0 & 13,100.0 & 0.0 & 0.0\\
\hline
48 & 12,000.0 & 8,000.0 & 0.0 & 12,000.0\\
\hline
49 & 0.0 & 126.0 & 0.0 & 0.0\\
\hline
50 & 1,323.0 & 0.0 & 3,969.0 & 0.0\\
\hline
51 & 1,170.0 & 1,170.0 & 0.0 & 780.0\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-8}the other parameter's values}
\centering
\begin{tabular}[t]{ccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{raw-material} \\
\cmidrule(l{3pt}r{3pt}){2-7}
  & 1 & 2 & 3 & 4 & 5 & 6\\
\midrule
price & 16.6 & 15.5 & 18.1 & 14.7 & 19.8 & 15.2\\
$\sigma_k$ (in kg) & 15,000.0 & 10,000.0 & 11,500.0 & 9,000.0 & 8,000.0 & 12,500.0\\
$z_{0k}$ (in kg) & 3,250.0 & 2,850.0 & 3,300.0 & 2,500.0 & 3,500.0 & 3,050.0\\
$m_{0k}$ (in kg) & 7,956,000.0 & 19,944,000.0 & 648,000.0 & 2,952,000.0 & 288,000.0 & 4,212,000.0\\
$ss$ (in kg) & 2,500.0 & 2,500.0 & 2,500.0 & 2,500.0 & 2,500.0 & 2,500.0\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}maxcap (in kg) = 1,427,000}\\
\end{tabular}
\end{table}

From Table 2 we know that raw material 4 must be purchased since item 49
and 50 can be produced just by using raw material 4. The price of raw
material 4 is the lowest one. But the minimal one-year order quantity is
the second smallest. So that we may guess that on the optimal solution,
\(x_4\) will have a big value but is not the biggest one among others.

\hypertarget{optimal-solution}{%
\subsection{Optimal solution}\label{optimal-solution}}

We solve the optimization problem by creating computer codes using R
language (version 4) where the optimization problem formulation and the
solution technique used are referred to dplyr {[}22{]} and ompr {[}23{]}
libraries. This program runs on a computer with the Linux Ubuntu 20 LTS
operating system with an Intel i7 8 Cores processor and 16 GB RAM.

The values of \(x_k,k \in \mathfrak{N},\) are given in the second column
of Table 6 in the following. The weekly deliveries are given on columns
4 up to 6. We see that the total one-month order quantity exceeds the
minimum one-month order quantity \(\sigma_k,\) so that set of
Constraints I is satisfied.

\caption{\label{tab:unnamed-chunk-9}Total order quantity and weekly deliveries}
\centering
\begin{tabular}[t]{cccccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{4}{c}{weekly deliveries (in kg)} \\
\cmidrule(l{3pt}r{3pt}){3-6}
Raw Material & Order Qty
(in kg) & Week 1 & Week 2 & Week 3 & Week 4\\
\midrule
1 & 192,649 & 6,553 & 65,295 & 81,722 & 39,079\\
2 & 543,385 & 354,839 & 23,595 & 96,122 & 68,829\\
3 & 90,742 & 41,092 & 26,550 & 14,400 & 8,700\\
4 & 56,508 & 33,264 & 209 & 18,369 & 4,666\\
5 & 52,958 & 42,608 & 10,350 & 0 & 0\\
\addlinespace
6 & 202,853 & 70,728 & 111,075 & 0 & 21,050\\
Total & 1,139,094 & 6,553 & 65,295 & 81,722 & 39,079\\
\bottomrule
\end{tabular}
\end{table}

Besides the values \(x_k\) above, we also get
\(\hat{x}_{ijk}, a_{ijk}, b_{ijk}\) and values \(z_{jk}\) in the optimal
solution. We have checked that set of \textbf{Constraints II -- V} are
satisfied by this optimal solution. For brevity, we do not present those
values here. We just present and discuss some of them, to show that the
remaining constraints are satisfied.

Most values of \(b_{ijk}\) are \(0.5\) which mean most of items are
produced by using a composition of two raw materials. The values of
\(b_{ijk}\) may vary from one week to another wee, as illustrated in
Table 7. The composition of raw materials for item 46 in week 1is
different from the composition in week 2. Furthermore, Table 7 shows us
that the proportions of raw materials used for producing an item are the
same. We have checked this property through all for all and for all so
that we are sure that set of \textbf{Constraints VI} are satisfied.

\caption{\label{tab:unnamed-chunk-10}the values of $b_{ijk}$ for $i = 45$ and $i = 46$}
\centering
\begin{tabular}[t]{cccccccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{6}{c}{raw-material} \\
\cmidrule(l{3pt}r{3pt}){3-8}
item & week & 1 & 2 & 3 & 4 & 5 & 6\\
\midrule
45 & 1 & 0.00 & 0.50 & 0.00 & 0.50 & 0.00 & 0.00\\
45 & 2 & 0.50 & 0.50 & 0.00 & 0.00 & 0.00 & 0.00\\
45 & 3 & 0.50 & 0.50 & 0.00 & 0.00 & 0.00 & 0.00\\
45 & 4 & 0.50 & 0.50 & 0.00 & 0.00 & 0.00 & 0.00\\
46 & 1 & 0.33 & 0.33 & 0.00 & 0.33 & 0.00 & 0.00\\
\addlinespace
46 & 2 & 0.50 & 0.50 & 0.00 & 0.00 & 0.00 & 0.00\\
46 & 3 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
46 & 4 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
\bottomrule
\end{tabular}
\end{table}

The following table shows the composition of raw materials for items 49
and 50. We can see that these items are produced by using raw material
4, which confirm the flexibility matrix in Table 3.

\caption{\label{tab:unnamed-chunk-11}the values of $b_{ijk}$ for $i = 49$ and $i = 50$}
\centering
\begin{tabular}[t]{cccccccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{6}{c}{raw-material} \\
\cmidrule(l{3pt}r{3pt}){3-8}
item & week & 1 & 2 & 3 & 4 & 5 & 6\\
\midrule
49 & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
49 & 2 & 0 & 0 & 0 & 1 & 0 & 0\\
49 & 3 & 0 & 0 & 0 & 0 & 0 & 0\\
49 & 4 & 0 & 0 & 0 & 0 & 0 & 0\\
50 & 1 & 0 & 0 & 0 & 1 & 0 & 0\\
\addlinespace
50 & 2 & 0 & 0 & 0 & 0 & 0 & 0\\
50 & 3 & 0 & 0 & 0 & 1 & 0 & 0\\
50 & 4 & 0 & 0 & 0 & 0 & 0 & 0\\
\bottomrule
\end{tabular}
\end{table}

The fulfillment of the safety stock constraint and the maximum capacity
constraint (set of \textbf{Constraints VII and VIII}) can be seen in the
following table.

\caption{\label{tab:unnamed-chunk-12}The fulfillment of the safety stock constraint and the maximum capacity constraint (set of Constraints VII and VIII)}
\centering
\begin{tabular}[t]{ccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{end-of-week stock (in kg)} \\
\cmidrule(l{3pt}r{3pt}){2-5}
Raw material & week 1 & week 2 & week 3 & week 4\\
\midrule
1 & 2,501 & 2,501 & 2,500 & 2,500\\
2 & 181,743 & 2,501 & 2,500 & 2,500\\
3 & 2,500 & 2,500 & 2,500 & 2,500\\
4 & 2,500 & 2,501 & 2,501 & 2,500\\
5 & 2,500 & 2,500 & 2,500 & 2,500\\
\addlinespace
6 & 2,500 & 2,500 & 2,500 & 2,500\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{conclusion-and-discussion}{%
\section{Conclusion and Discussion}\label{conclusion-and-discussion}}

In this paper we present mixed-integer linear program (MILP) for
raw-material selection and composition, and order allocation problem
faced by a beverage company. We performed a number of numerical
experimentation to check the optimal solutions for various demands and
for various objective functions. From these experimentation we are sure
that our MILP gives the desired optimal solutions.

It should be noticed that the definition of the objective function which
accommodate the minimum one-year order quantity contract yields a
balancing of purchase price criteria and the minimum one-year order
quantity criteria. In the following table we represent the optimal
solutions obtained by using different objective functions. Notice that
the total raw materials purchased in all optimal solutions are the same,
i.e.~1,139,094 kg.

Table 10 The different of the optimal solutions obtained by using
different objective functions.

\begin{itemize}
\tightlist
\item
  Objective function 1:
\end{itemize}

\[
\frac{1}{2} hc \sum_{j \in M} \sum_{k \in \mathfrak{N}} (z_{(j-1)k} + z_{jk} + \hat{x}_{jk})
\]

\begin{itemize}
\tightlist
\item
  Objective function 2:
\end{itemize}

\[
\frac{1}{2} hc \sum_{j \in M} \sum_{k \in \mathfrak{N}} (z_{(j-1)k} + z_{jk} + \hat{x}_{jk}) + \sum_{k \in \mathfrak{N}} c_k x_k
\]

\begin{itemize}
\tightlist
\item
  Objective function 3:
\end{itemize}

\[
\frac{1}{2} hc \sum_{j \in M} \sum_{k \in \mathfrak{N}} (z_{(j-1)k} + z_{jk} + \hat{x}_{jk}) + \sum_{k \in \mathfrak{N}} c_k x_k - \sum_{k \in \mathfrak{N}} \alpha_k mo_k x_k
\]

\caption{\label{tab:unnamed-chunk-13}Optimal solution comparison between different objective functions}
\centering
\begin{tabular}[t]{cccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Optimal solution} \\
\cmidrule(l{3pt}r{3pt}){2-4}
Raw material & obj function 1 & obj function 2 & obj function 3\\
\midrule
1 & 276,780 & 363,486 & 192,649\\
2 & 464,388 & 532,404 & 543,385\\
3 & 35,645 & 20,402 & 90,742\\
4 & 214,811 & 60,124 & 56,508\\
5 & 29,400 & 16,888 & 52,958\\
\addlinespace
6 & 118,070 & 145,791 & 202,853\\
Total & 1,139,094 & 1,139,094 & 1,139,094\\
\bottomrule
\end{tabular}
\end{table}

From Table 10 we see if we just use the purchase price in the objective
function, raw material 4 is purchased with the biggest amount. But since
in the distribution of \(mo_k\) raw material 4 has the second smallest
value, then if we consider this distribution in the objective function,
raw material 4 is purchased with a smaller amount.

The last thing to be discussed is the multiplier parameter \(\alpha_k\).
These parameters should be set as a positive number in early months of
the year, when the minimum one-year order quantity contracts are still
far away to be fulfilled. As soon as the contract for raw material \(k\)
is fulfilled, we can set \(\alpha_{k=0}\).

\hypertarget{acknowledment}{%
\section{Acknowledment}\label{acknowledment}}

The research in this paper is partially funded by the Penelitian Tesis
Magister research grant, Ministry of Research and Technology of the
Republic of Indonesia.

@@

\leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Wickham, H., François, R., Henry, L., Müller, K., \&
Vaughan, D. (2023). \emph{Dplyr: A grammar of data manipulation}.}

\leavevmode\vadjust pre{\hypertarget{ref-ompr}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Schumacher, D. (2022). \emph{Ompr: Model and solve mixed
integer linear programs}. Retrieved from
\url{https://github.com/dirkschumacher/ompr}}
